---
title: "06.02 Information Theory and Model Performance"
author: "JP"
date: "4/3/2019"
output: html_document
---

## Overview: 
To balance between over and underfitting you must first choose a *criterion of model performance*. You must choose a *target* that you want the model to perform well at. Information theory provides a common and useful target, the *out-of-sample deviance*.

The path to understanding the relevance of out-of-sample deviance is not direct. Here are the steps ahead. 
    1. establish that joint probability, not average probability, is the right way to judge model accuracy. 
    2. use information theory to establish a measurement scale for distance from perfect accuracy. 
    3. establish deviance as an approximation of relative distance from perfect accuracy. 
    4. establish that it is only deviance out-of-sample that is of interest.

```{r global options, include=FALSE}
knitr::opts_chunk$set(
  fig.align='center', dpi = 300, 
  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE
)
```

```{r packages and parameters}
library(magrittr)
library(modelr)
library(tidyverse)
```