---
title: "Distribution Functions in R"
output: html_document
---

`runif(n, min, max)`

`dunif(x, min, max)` calculates the probability of a variable taking on value within a specified range defined by ... . Note this function only seems to be used within graphs or within other functions. It will not return a useful value on its own. 

```{r}
x <- seq(from = -10, to = 60, by = 1)
dunif(x = c(.25, .5), min = 0, max = 1)
```

What does this demonstrate
```{r}
dunif(x = 10, min = 0, max = 120) # which is 121 in length
1/120
```

```{r}
a <- 0
b <- 0.5

punif(b) - punif(a)
```

```{r}
# Probability computed using the integrate() function of the pdf dunif()
integrate(
  f = dunif, 
  lower = 0.1, 
  upper = 0.5
)
```

First Google hit with [code](http://faculty.las.illinois.edu/lylek/Chico/pdf&calc.html)

[U of Arizona site](http://www.u.arizona.edu/~kuchi/Courses/MAT167/Files/LH_LEC.0420.RandVars.Normal.pdf) says that dunif() is really only useful for graphing, not for directly calculating probabilities. 

In his example below I see that `dunif()` works even though x is undefined. 
```{r}
curve( 
  expr = dunif(x , min = 2 , max = 6), 
  from = 0, to = 8,
  ylim = c(0 , 0.5), 
  ylab = "f(x)", 
  main = "Uniform Density f(x)"
)
```

# Normal Distributions
```{r}
tibble(x = seq(from = 100, to = 250, by = .1)) %>% 
  ggplot(aes(x = x, y = dnorm(x, mean = 178, sd = 20))) +
  geom_line() +
  ylab("density")
```

Here `dnorm()` takes the 150^10 data points in `x` and distributes probability across all those points such that plotting y on x produces a normal distribution. 

```{r}
dnorm(x, 178, 20) %>% length()
```





