---
title: "Bayesian Models"
author: "JP"
date: "4/17/2019"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

# Probability Distributions
What is a `probability distribution`? It is just a mathematical function that outputs the probabilities that different outcomes will result from an experiment. 

Intuitively, if I have 10 events and a .3 probability of success on each event, then I can form a probability distribution for `Binomial(n, p)`.
```{r}
(binomial_10_.3 <- dbinom(0:10, 10, .3))

tibble(
  x = as.factor(0:10),
  y = binomial_10_.3
) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_col()
```

Intuitively I usally think of a distribution as being the relative frequency of the different outcomes. I often think of this as a histogram, but I can see now that such a histogram could be mathematically described by function like `dbinom()` when the function inputs the vector of all possible discrete outcomes. 

The probability of events in a `discrete probability distribution` can be described by a `probability mass function`.

The *binomial probability distribution* is the discrete probability distribution of the `number of successes` in n independent trials, each with a binary outcome. 
```{r}
dbinom(
  x = 0:10,  # vector of all possible counts of successful trials
  size = 10, # number of trials (n)
  prob = .3  # probability of success
)
```

What does this outcome of the binomial distribution 
