---
title: "Distribution Functions in R"
output: html_document
---

`runif(n, min, max)`

`dunif(x, min, max)` will output the y-axis height at x of the uniform distribution between `min` and `max`. 

```{r}
dunif(x = c(.25, .5), min = 0, max = 1)
```

But note that this y-axis output from the `uniform density function` is not the probability that the random variable will equal x, it is just the height at the y-axis when the random variable equals x. Further computation is necessary to determine probabilities of x taking on specified values, and those values must be specified as a range when x is continuous. 

Note that the y-axis height associated with any x value is equal to 1 / (the range of the uniform distribution).
```{r}
dunif(x = 10, min = 0, max = 120)
dunif(x = 10.5, min = 0, max = 120)
1/120
```

```{r}
a <- 0
b <- 0.5

punif(b) - punif(a)
```

```{r}
# Probability computed using the integrate() function of the pdf dunif()
integrate(
  f = dunif, 
  lower = 0.1, 
  upper = 0.5
)
```

First Google hit with [code](http://faculty.las.illinois.edu/lylek/Chico/pdf&calc.html)

[U of Arizona site](http://www.u.arizona.edu/~kuchi/Courses/MAT167/Files/LH_LEC.0420.RandVars.Normal.pdf) says that dunif() is really only useful for graphing, not for directly calculating probabilities. 

In his example below I see that `dunif()` works even though x is undefined. 
```{r}
curve( 
  expr = dunif(x , min = 2 , max = 6), 
  from = 0, to = 8,
  ylim = c(0 , 0.5), 
  ylab = "f(x)", 
  main = "Uniform Density f(x)"
)
```

# Normal Distributions
```{r}
tibble(x = seq(from = 0, to = 100, by = .1)) %>% 
  ggplot(aes(x = x, y = dnorm(x, mean = 50, sd = 15))) +
  geom_line() +
  ylab("density")
```

Here `dnorm()` takes the 150^10 data points in `x` and distributes probability across all those points such that plotting y on x produces a normal distribution. 

```{r}
dnorm(x, 50, 15) %>% length()
```

```{r}
tibble(x = seq(from = 0, to = 100, by = 1)) %>% 
  ggplot(aes(x = x, y = dnorm(x, mean = 50, sd = 15))) +
  geom_line() +
  ylab("density")
```



