---
title: "The Probability Density Function"
author: "JP"
date: "4/16/2019"
output: html_document
---

```{r}
library(knitr)
library(tidyverse)
```

```{r}
file_normal_pdf <- here::here("static/images/normal_pdf.png")
```

```{r deviance, echo=FALSE, out.width="400px", include=TRUE}
knitr::include_graphics(file_normal_pdf)
```

The `probability density function (PDF)` outputs the height of the y-axis on the probability density curve at the provided x value. The PDF does NOT output the probability that a random variable will take on a particular value of x. To calculate the probability of x taking on a values can only be calculated as x falling within a range of values, because the probabillity of a continuous random variable taking on a specific value is 1/inf. 

In contrast, the `binomial probability distribution` has a `probability mass function (PMF)` rather than a density function because it's outputs are discrete.  
```{r}
# outputs Pr(1 head in 1 flip)
success_n <- 1 
trials_n <- 1
prob_success <- .5
dbinom(success_n, trials_n, prob_success)

# outputs probability of 5 heads in 10 flips
success_n <- 5 
trials_n <- 10
prob_success <- .5
dbinom(success_n, trials_n, prob_success)
```


